---
title: "JASA Sharing Reproducible Materials over Github"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


This GitHub repository contains a template structure for author(s) who
submit to JASA (either Applications and Case Studies or Theory and Methods) to include materials to
reproduce analyses, visualizations, and tables.

We provide this template as a default structure that we think could be useful for many projects, either as is or with modifications by authors. However, the template is intended to be helpful and is by no means required of authors. Authors should consult [our reproducibility guide](https://jasa-acs.github.io/repro-guide) for details on what is required of reproducibility materials submitted with JASA revisions (not required upon initial submission). 

## Why is template repository this useful? 

The purpose of this template repository is to provide a mechanism for 
author(s) to share their materials via a Git repository, hosted on a cloud-based repository manager such as GitHub or GitLab. This provides the following advantages for author(s): 

1. Analyses (including code, narrative text, output, plots, etc) can be version controlled (or branched or forked) allowing original author(s) to continue to develop the analyses or other data analysts to build off the analyses. Also iterations and changes to the analysis are then available via the Git commit history. 
2. Materials are easily available to other researchers.
3. Preparing a repository also makes it easy for the JASA associate editors for reproducibility to copy the materials for a JASA article into the JASA GitHub repository.
4. Others? 

## How does the process work? 

### Step 1 

Author(s) create a public GitHub repository by 

1. Forking this template repository 
2. Using `git clone` and removing the `.git` file
3. (need to add steps to init a new repository and push to github/gitlab/etc.)

Alternatively, author(s) can manually create their own repository with the structure of this repository (possibly with modifications). 

### Step 2 

Author(s) edit (or replace) the manuscript template file and add their data, code, and other files.

**Importantly, the authors should provide an overview of how to carry out the analyses presented in their manuscript in the README.md of their repository, replacing the content in this file.** This overview would generally refer to scripts/code files that execute the analyses and are placed either in the main directory or the `code` subdirectory. The *Workflow* section of the ACC form should refer to this README.md as containing the instructions for how to reproduce the analyses.

### Step 3

Author(s) use `git commit` to track changes over time and use `git push` to push changes to a repository on the author(s) personal GitHub account. 

### Step 4 

Author(s) submit a link to their GitHub repository as part of the [JASA Reproducibility review process](https://jasa-acs.github.io/repro-guide/). 

### Step 5

JASA Associate Editors for Reproducibility will review the materials in the personal GitHub repository of the authors and submit a reproducibility review as part of the standard JASA review process. Authors have the opportunity to respond to the review by making changes and pushing their changes to their personal GitHub repository. 

**Should reviewers/editors be allow to provide pull requests?**

*My initial two cents is that we hold off on PRs // CJP*

### Step 6 

Once the manuscript is accepted, the materials in the author(s) personal GitHub repository will be copied to the [JASA repository](https://github.com/jasa-acs). 


## Description of template structure using R 

Two preferred file structures for submissions are shown below. 
The goals in prescribing this structure are to make
it easier for the reproducibility reviewer to confirm the materials are
sufficient for reproducing the results as well as facilitating automated
generation of the outputs via Docker, Singularity, or Github Actions.

## Reproduciblity materials only

The first is for the case where reproducibility materials are being provided and are
separate from the manuscript. 


```{r echo = FALSE}
library(listdown)
file_type <- function() {
  a = 0
  class(a) <- "file"
  a
}
dir_type <- function() {
  a = 0
  class(a) <- "dir"
  a
}

`project directory` <- list(
  ".here" = file_type(),
  "README.md" = file_type(),
  "renv/" = dir_type(),
  "manuscript/" = dir_type(),
  "data/" = dir_type(),
  "code/" = dir_type(),
  "output/" = dir_type()
)
ld_cc_dendro(`project directory`)
```

## Reproducible document

The second is for manuscripts written as
R Markdown documents (this repository).

```{r echo = FALSE}
`project directory` <- list(
  "manuscript.rmd" = file_type(),
  "renv/" = dir_type(),
  "preprocessing/" = dir_type(),
  "data/" = dir_type()
)
ld_cc_dendro(`project directory`)
```

## Guidance on the use of reproducible environments

Submissions may include the use of reproducible environments capturing
state of a machine generating manuscript artifacts and even the manuscript
itself. Here we discuss two types of reproducible environments and their use.

### Package environments

Package environments capture the set of packages used by a programming language
needed to generate output. The R programming language has `renv`, 
`switchr` and others to accomplish this, Python has `venv`, `conda` and others, 
and Julia has native support (through the `Pkg` package). When submitting 
these types of environments, the following are suggested.

1. Provide documentation indicating the language environment and the version
was used to produce outputs.
2. Use a single package environment for all reproducible content.
3. Prefer packages from package archives (CRAN, Bioconductor, RForge.net for 
example).
4. If you use packages from a code repository (Github, Gitlab, etc.) then
use a release version. If none is available fork the repository and provide a 
release.

### Virtual environments

Virtual capture like docker and singularity for example, capture the entire 
computing environment in which computations were performed. In general, they
are a more robust solution, capable of taking a "snapshot" of a machine including
any system-level utilities and external libraries needed to perform you computation.
They have the advantage that reproducing materials mean running the virtual
environment, rather than recreating the programming language environment and
may be preferred. When submitting these types of environments, the following are suggested.

1. Provide a single saved image with shared folder referencing the reproducibility
file structure described above.
2. If a single saved image is not being submitted, be aware of the suggestions
provided in the [Package environments] section above.

## References

Gentleman, Robert, and Duncan Temple Lang. "[Statistical Analyses and Reproducible Research](http://biostats.bepress.com/cgi/viewcontent.cgi?article=1001&context=bioconductor)." (2004).

Gentleman, Robert. "[Reproducible research: a bioinformatics case study](https://www.degruyter.com/document/doi/10.2202/1544-6115.1034/html)." Statistical applications in genetics and molecular biology 4.1 (2005).

Marwick, Ben, and Bryan, Jennifer, and Attali, Dean, and Hollister, Jeffrey W. [rrrpkg Github Page](https://github.com/ropensci/rrrpkg).


